Hydrodynamics of two vesicles interacting via a Van der Waals potential

### 2019-01-07 vesicle_code/docs/adhesion/adhesion.tex
fixed extensional snapshot figures

\begin{figure}[htp]
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image01.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image02.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image03.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image04.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi9em2_ra080_image05.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image06.png}
  \caption{Two vesicles in an extensional flow.  The reduced area is
  $0.8$, the adhesion strength is $0.7$, and the adhesion length scale
is $0.4$, extensional rate is $\chi = 0.05$.}
\end{figure}

\begin{figure}[htp]
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image01.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image02.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image03.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image04.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image05.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image06.png}
  \caption{Two vesicles in an extensional flow.  The reduced area is
  $0.8$, the adhesion strength is $0.7$, and the adhesion length scale
is $0.4$, extensional rate is $\chi = 0.1$.}
\end{figure}

>>>>

\begin{figure}[htp]
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image01.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image02.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image03.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image04.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image05.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image06.png}
  \caption{Two vesicles in an extensional flow.  The reduced area is
  $0.8$, the adhesion strength is $0.7$, and the adhesion length scale
is $0.4$, extensional rate is $\chi = 0.05$.}
\end{figure}

\begin{figure}[htp]
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image01.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image02.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image03.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image04.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image05.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image06.png}
  \caption{Two vesicles in an extensional flow.  The reduced area is
  $0.8$, the adhesion strength is $0.7$, and the adhesion length scale
is $0.4$, extensional rate is $\chi = 0.1$.  After time $t=400$, the
  vesicles extensional rate has overcome the adhesive force, and the
  vesicles continue to separate.}
\end{figure}
